European or American? A re-examination of the transatlantic influence over the IMF

### 2025-08-06 manuscript/manuscript.qmd
Add African table to manuscript
Add GPT robustness intro

## Robustness: Continental Preference?

@@

>>>>

## Robustness Checks

While our baseline results indicate that European powers exert substantial influence over IMF lending outcomes, two common explanations in the literature could potentially account for these patterns without implying broad, institutionalised influence.

First, European powers may favour geographically proximate borrowers — in other words, a continental preference — leading to disproportionately favourable treatment of European recipients. Second, given the historical legacy of colonialism, particularly in Africa, European powers might be more inclined to support former colonies (colonial preference), especially those with enduring political, economic, or cultural ties.

In this section, we test both explanations by interacting our measure of European influence with indicators for European and African recipients, respectively. If either hypothesis holds, we would expect the interaction terms to be positive and significant, indicating stronger European influence in those contexts. As shown below, neither hypothesis is supported: in both cases, the interaction terms are insignificant or negative, and our core finding — that European influence is associated with more favourable IMF lending outcomes — remains robust across the recipient groups. This suggests that European influence is not geographically or historically confined, but instead reflects a global institutional role within the IMF.

### Continental Preference?

@@

### Colonial Preference?

```{r}
#| label: tbl-results-africa
#| tbl-cap: Effects of US and European Influence on IMF Lending Outcomes (1980–2010), Separating African and Non-African Recipients
#| tbl-pos: H
load('save/regTable_africa.RData')
resultsTable |> tinytable::theme_tt("resize", width = 1)
```
